---
#title: "Exploratory Analysis"
#author: "Abigail Babila", "Emma Esteban", "Jingjun Zhao"
date: "1/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Exploratory Analysis: Understanding Global Healthcare Inequalities by Country Debt

## Report Summary
```{r message=FALSE,warning=FALSE}
library("knitr")
library("dplyr")
library("tidyverse")
source("../source/summary_info1.R")
```
This is a brief report regarding the influence of international debts over government' health spending and how that negatively influences local citizen health. It looks at data for `summary_info$num_countries` countries. This page compares the health spending and health situation between countries all over the world, `summary_info$num_in_debt` of which are _in debt crisis_ according to the Jubilee Debt Campaign (JDC). While chart 1 maps global differences in health spending, chart 2 furthers our argument by showing the correlation between debt and health spending. Currently, the country that uses the greatest percent of government expenditure on health, `summary_info$greatest_country`, has a net creditor score of `summary_info$greatest_country_net`. Also, the data looks at maternal mortality rate as an indicator to show how countries in debt impact individual health. Currently, the country with the lowest net creditor/debtor score, `summary_info$most_in_debt`, has a maternal mortality rate of `summary_info$most_in_debt_mmr`. Our analysis aims to prove how financial actors in government play a role in citizen health and health care.

## Summary Table
#In this table, we included all the important indicators that helps us prove the correlation between international debts and citizens' well beings, which is also a summary for all the essential indicators we used for the following chart. We want use this table to show the dimension including debts, government health spending, and health indicators that we include in this page, and also how many countries we are included in our research.
```{r message=FALSE,warning=FALSE}
library("dplyr")
library("tidyverse")
source("../source/summary_table.R")
print(Summary_data)
```

## Chart 1: Maps

#### Government Heath Expenditure per capital and Health Spending as a Share of Total Government Expenditure
##To compare the each countries' government health spending per capital, this is a global map showing the health spending in 2019. After that, we have a map showing the government health spending as share of the overall government expenditure
```{r message=FALSE,warning=FALSE}
options(repos=structure(c(CRAN="YOUR FAVORITE MIRROR")))
install.packages("dplyr", dependencies = TRUE)
install.packages("ggplot2", dependencies = TRUE)
library("dplyr")
library("ggplot2")
install.packages("maps",dependencies = TRUE)
install.packages("viridis", dependencies = TRUE)
require("viridis")
library("maps")
require(maps)
source("../source/per capital.R")
```



## Chart 2: Scatter Plot

#### Government Debt and Health Spending
```{r message=FALSE,warning=FALSE}
install.packages("plotly", dependencies = TRUE)
library("dplyr")
library("tidyverse")
library("ggplot2")
library("plotly")
require(plotly)
source("../source/chart_2.R")
ggplotly(plot)
```
This chart is a scatter plot showing the relationship between a country's government debt and government health spending. Each point represents a country. On the x-axis is the a numeric indicator for net creditor(+) or debtor(-) of that country from 2020. On the y-axis is the health spending as a percent of total government expenditure. This number is taken form the most-recent year of data collection, which most are from 2019 with a few from 2018. The color of each point tells you what the level of debt risk calculated by the Jubilee Debt Campaign. Hover over a point for more specific statistical information. The line shows a positive trend, with a dip where countries are neither a very far into debt or are large creditors.

## Chart 3: Barplot
#### Financial Status and Health Indicators
```{r message=FALSE,warning=FALSE}
install.packages("hrbrthemes", dependencies = TRUE)
library("hrbrthemes")
library("dplyr")
library("tidyverse")
library("ggplot2")
source("../source/MMR.R")

```
This barplot depicts the maternal mortality rate of women across different countries around the world with different financial statuses. Based on this data, countries with lower incomes and less access to healthcare have a larger negative effect on women’s health which poses as a bigger risk.

